Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-14 analysis/paper/paper.Rmd
Update graphs using DAI for x-axis

Disease severity values were converted to the midpoint percentage value of the disease assessment scale. Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity. As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using multivariate generalised linear mixed models implemented in the `MCMCglmm` package [@MCMCglmm2010] in the R programming environment [@R2018].

@@

ggplot(RAW_data,
       aes(x = ASMT,
           y = TShB_incidence,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_y_continuous(labels = function(x) paste0(x*100), limits = c(0, 1)) +
  scale_shape_discrete(labels = c(expression(N[0]),
                                  expression(N[1]),
                                  expression(N[2]),
                                  expression(N[3]),
                                  expression(N[4]))) +
  scale_linetype_discrete(labels = c(expression(N[0]),
                                     expression(N[1]),
                                     expression(N[2]),
                                     expression(N[3]),
                                     expression(N[4]))) +
  ylab("Tiller Sheath Blight Incidence (%)") +
  xlab("Assessment") +
  facet_grid(WMGT ~ YEAR) +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom") +
  guides(linetype = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))
```

@@

ggplot(RAW_data,
       aes(x = ASMT,
           y = PERC_TIL_ShB,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_shape_discrete(labels = c(expression(N[0]),
                                  expression(N[1]),
                                  expression(N[2]),
                                  expression(N[3]),
                                  expression(N[4]))) +
  scale_linetype_discrete(labels = c(expression(N[0]),
                                     expression(N[1]),
                                     expression(N[2]),
                                     expression(N[3]),
                                     expression(N[4]))) +
  ylab("Tiller Sheath Blight Severity (%)") +
  xlab("Assessment") +
  facet_grid(WMGT ~ YEAR) +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom") +
  guides(linetype = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))
```

@@

ggplot(RAW_data,
       aes(x = ASMT,
           y = PERC_LEAF_ShB,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_shape_discrete(labels = c(expression(N[0]),
                                  expression(N[1]),
                                  expression(N[2]),
                                  expression(N[3]),
                                  expression(N[4]))) +
  scale_linetype_discrete(labels = c(expression(N[0]),
                                     expression(N[1]),
                                     expression(N[2]),
                                     expression(N[3]),
                                     expression(N[4]))) +
  ylab("Leaf Sheath Blight Severity (%)") +
  xlab("Assessment") +
  facet_grid(WMGT ~ YEAR) +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom") +
  guides(linetype = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))
```

>>>>

Because the data were collected on an ordinal scale, but not evenly spaced, the data are converted to the midpoint value of the percent range for severity. Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity. As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using multivariate generalised linear mixed models implemented in the `MCMCglmm` package [@MCMCglmm2010] in the R programming environment [@R2018].

@@

ggplot(RAW_data,
       aes(x = DAI,
           y = TShB_incidence,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_y_continuous(labels = function(x) paste0(x*100), limits = c(0, 1)) +
  scale_shape_discrete(labels = c(expression(N[0]),
                                  expression(N[1]),
                                  expression(N[2]),
                                  expression(N[3]),
                                  expression(N[4]))) +
  scale_linetype_discrete(labels = c(expression(N[0]),
                                     expression(N[1]),
                                     expression(N[2]),
                                     expression(N[3]),
                                     expression(N[4]))) +
  ylab("Tiller Sheath Blight Incidence (%)") +
  xlab("Days After Inoculation") +
  facet_grid(WMGT ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom") +
  guides(linetype = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))
```

@@

ggplot(RAW_data,
       aes(x = DAI,
           y = PERC_TIL_ShB,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_shape_discrete(labels = c(expression(N[0]),
                                  expression(N[1]),
                                  expression(N[2]),
                                  expression(N[3]),
                                  expression(N[4]))) +
  scale_linetype_discrete(labels = c(expression(N[0]),
                                     expression(N[1]),
                                     expression(N[2]),
                                     expression(N[3]),
                                     expression(N[4]))) +
  ylab("Tiller Sheath Blight Severity (%)") +
  xlab("Days After Inoculation") +
  facet_grid(WMGT ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom") +
  guides(linetype = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))
```

@@

ggplot(RAW_data,
       aes(x = DAI,
           y = PERC_LEAF_ShB,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_shape_discrete(labels = c(expression(N[0]),
                                  expression(N[1]),
                                  expression(N[2]),
                                  expression(N[3]),
                                  expression(N[4]))) +
  scale_linetype_discrete(labels = c(expression(N[0]),
                                     expression(N[1]),
                                     expression(N[2]),
                                     expression(N[3]),
                                     expression(N[4]))) +
  ylab("Leaf Sheath Blight Severity (%)") +
  xlab("Days After Inoculation") +
  facet_grid(WMGT ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom") +
  guides(linetype = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))
```
